Self Regulation Ontology Retest Data Report

### 2017-11-20 code/SRO_Report.Rmd
cleaning up notes

@@

hddm_refits %>%
  gather(dv, value, -sub_id) %>%
  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
  rename(fullfit = value.y, refit = value.x) %>%
  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
  filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
  ggplot(aes(fullfit, refit))+
  geom_point(aes(color=rt_acc))+
  facet_wrap(~raw_fit)+
  theme_bw()+
  geom_abline(slope=1, intercept=0)+
  xlab("Fit on full sample")+
  ylab("Fit on retest sample")+
  theme(legend.title = element_blank())
```

@@

>>>>

NOTE: DO THIS ON AN EXAMPLE TASK AND LEAVE TO THE READER TO DO

@@

ggplotly(hddm_refits %>%
  gather(dv, value, -sub_id) %>%
  left_join(hddm_fullfits, by = c("sub_id", "dv")) %>%
  rename(fullfit = value.y, refit = value.x) %>%
  left_join(measure_labels[,c("dv", "raw_fit", "rt_acc")], by="dv") %>%
  filter(rt_acc %in% c("drift rate","non-decision", "threshold")) %>%
  ggplot(aes(fullfit, refit, label=dv))+
  geom_point(aes(color=rt_acc))+
  facet_wrap(~raw_fit)+
  theme_bw()+
  geom_abline(slope=1, intercept=0)+
  xlab("Fit on full sample")+
  ylab("Fit on retest sample")+
  theme(legend.title = element_blank()),
  label=dv)
```

```{r}
hddm_refits %>%
  filter(adaptive_n_back.hddm_drift<0)
  # ggplot(aes(adaptive_n_back.EZ_drift))+
  # geom_histogram()

hddm_fullfits %>%
  filter(dv == "adaptive_n_back.hddm_drift" & value <0)
```

@@

The above graph suggests that the median reliability estimate does not change depending on the sample size. There is a degree of counterintuitiveness to that statement. One might expect less reliable parameter estimates for smaller sample sizes.

The reliability of a measure depends on the different sources of variability. It would be larger the larger the between subject variability (BSV) is (and the lower within subject, WSV, and error variances, ERV, are). Larger sample sizes do not necessarily imply larger BSV. If there is a true BSV for the whole sample then BSV's of subsamples would have distribution that would be centered around this value with some variance. This variance would be smaller the larger the sample size. Because the distribution is centered around the true BSV the median reliability estimate from 100 samples would not deviate much as we see in the above graph. But the variance of that reliability estimate would. Specifically the variance of the reliability estimates should decrease with increasing sample size. Below we plot this for one task (for visualization ease). The lower end of the error bars in the first quantile, the point is the median and the upper bound is the last quantile of the reliability estimates for varying sample sizes. Indeed, we find the predicted pattern of decreasing variance in reliability estimates depending on sample size.

```{r}
tmp %>%
  select(dv, N, icc_median, icc_2.5, icc_97.5) %>%
  filter(grepl("stroop", dv)) %>%
  ggplot(aes(N, icc_median, color = dv))+
  geom_point()+
  geom_errorbar(aes(ymin = icc_2.5, ymax = icc_97.5))+
  theme_bw()+
  theme(legend.position = "none")+
  ylab("ICC")
```
